Detecting distributional differences between temporal granularities for exploratory time series analysis

### 2021-05-30 paper/main.Rmd
changing abstract

abstract: |
 Periodic patterns or associations in large univariate time series data could be discerned by analysing the behaviour across cyclic temporal granularities, which are temporal deconstructions accounting for repetitive behaviour. The temporal granularities form ordered categorical variables and display of distributions of the univariate response variable across two or more combinations of these categorical variable can help explore periodicities, patterns and anomalies. A  pair of granularities that can be meaningfully examined together are called “harmonies” and the ones which cannot be are called “clashes”. Even after excluding clashes, the list of harmonies that could potentially be displayed is huge and hence overwhelming for human consumption. This work provides a methodology to screen the most informative graphics from the plethora of choices by introducing a distance measure that could be compared across harmonies with varied levels and data sets. Moreover, this distance measure could also be used to rank the s = ted harmonies basis how well they capture the variation in the measured variable. All the methods are implemented in the open source R package `hakear`.

>>>>

abstract: |
 Patterns or associations in large univariate time series data could be explored by analyzing the behavior across cyclic temporal granularities, which are temporal deconstructions accounting for repetitive behavior, for eg, hour-of-the-day, work-day/weekend, or holidays. This way of exploring time series analysis, however, presents itself with a plethora of displays that are potentially overwhelming for human consumption. This work provides a methodology to screen and rank the displays that are most informative in discerning distributional differences. This is done by introducing a distance measure for one or a pair of cyclic granularities that could be compared across different levels and data sets. All the methods are implemented in the open-source R package `hakear`.
